Summary Tables

### 2020-02-20 summary_tables_outcomes.Rmd
Use datatable to select columns

>>>>

### Test DT

```{r dt}

fname <- "whw"

DT::datatable(td, 
                  extensions = 'Buttons',
                  escape = FALSE,
                  rownames = FALSE,
                  options = list(dom = 'Bfrtip',
                                 buttons = 
                                   list('colvis', list(
                                     extend = 'collection',
                                     buttons = list(list(extend='csv',
                                                         filename = fname),
                                                    list(extend='excel',
                                                         filename = fname)),
                                     text = 'Download'
                                   )),
                                 scrollX = TRUE,
                                 pageLength = nrow(td),
                                 order=list(list(2,'desc'))))
```
